SPARQL on the open, decentralised Web

### 2016-06-05 dissertation/index.tex
Fix citations; new label on PRM selectivity
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@393 43ef1190-90fd-4dd7-a769-d0121f02b80e
Add refs
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@398 43ef1190-90fd-4dd7-a769-d0121f02b80e
fixups
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@400 43ef1190-90fd-4dd7-a769-d0121f02b80e
add machinelearning bib
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@403 43ef1190-90fd-4dd7-a769-d0121f02b80e
Say intro
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@406 43ef1190-90fd-4dd7-a769-d0121f02b80e
Add new dis

\documentclass[a4paper, 12pt, draft]{scrartcl}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[utf8]{inputenc}
\usepackage{multirow}
\usepackage{times}
\usepackage{listings}
\usepackage{supertabular}
\usepackage{cite}
\include{notasjon}
\include{helpers}
%\usepackage[pdftex,linktocpage,ps2pdf,dvips]{hyperref}

\begin{document}
\title{Dissertation}
\author{Kjetil Kjernsmo}
%\institute{Department of Informatics,
%Postboks 1080 Blindern,
%0316 Oslo, Norway}

@@

\input{introsota}

\bibliography{selectivity}
\bibliographystyle{plainnat}

>>>>

\documentclass[a4paper, 12pt, draft]{report}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{multirow}
%\usepackage{times}
\usepackage{listings}
\usepackage{supertabular}
\usepackage{cite}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage[obeyDraft]{todonotes}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}

\include{notasjon}
\include{helpers}
\usepackage[pdftex,linktocpage]{hyperref}
\hyperbaseurl{https://github.com/}

\newtheorem{problem}{Problem}[subsection]

\begin{document}
\title{SPARQL on the open, decentralised Web}
\author{Kjetil Kjernsmo}
%\institute{Department of Informatics,
%Postboks 1080 Blindern,
%0316 Oslo, Norway}

@@

\begin{abstract}
  This dissertation discusses a broad range of problems concerning the
  use of the SPARQL query language on the open, public Web. It is
  motivated from seeing decentralisation of data and infrastructure as
  an important social goal, and SPARQL as an enabling technology to
  solve problems using the Semantic Web. The dissertation makes
  contributions in hypermedia, where RDF is used to create a format
  that can tell humans and machines alike how to manipulate resources
  on the Web; philosophy of science, where important foundational
  problems around how to create valid knowledge and objectivity is
  discussed; statistical methods that better satisfies the
  requirements from philosophy of science than current practice; how
  to improve developer efficiency with novel programming paradigms;
  and finally how caching infrastructure in the Internet may be used
  to make query answering across the Web more robust.
\end{abstract}

\tableofcontents

\chapter{Introduction}

\input{introdefhistory}
\input{motivation}
\input{related}
\input{problems}
\input{papersincontext}
\input{cache-proxy}

\bibliography{management,dataprofiles,federation,dynamicity,hypermedia,specs,webarch,practical,semweb,caching,critisism,data,philosophy,benchmarks,rfc,programming,egne,optimization}
\bibliographystyle{plain}
